A Toolbox for Manipulating and Assessing Color Palettes

### 2019-08-28 pkg/colorspace/paper/Toolbox/article.Rmd
rebuilt pkgdown site with modified specplot and version 1.4-2
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/colorspace@505 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

```{r hcl-palettes, echo = TRUE, eval = FALSE}
library("colorspace")
hcl_palettes(plot = TRUE)
```
```{r hcl-palettes, echo = FALSE, fig.height = 6.75, fig.width = 12, fig.cap = "Brief overview of available predefined palettes in \\pkg{colorspace}."}
library("colorspace")
hcl_palettes(plot = TRUE, mar = c(0.1, 7, 0, 0), line = 6)
```

@@

```{r hcl-palettes-sequentialm, fig.width = 8.5, fig.height = 9.0, fig.cap = "Prespecified sequential multi-hue HCL palettes available in \\code{sequential\\_hcl()} in \\pkg{colorspace}."}
hcl_palettes("sequential (multi-hue)", n = 7, plot = TRUE)
```

>>>>

```{r hcl-palettes-0, echo = TRUE, eval = FALSE}
library("colorspace")
hcl_palettes(plot = TRUE)
```
```{r hcl-palettes, echo = FALSE, fig.height = 6.75, fig.width = 12, fig.cap = "Brief overview of available predefined palettes in \\pkg{colorspace}."}
library("colorspace")
hcl_palettes(plot = TRUE, mar = c(0.1, 7, 0, 0), line = 6)
```

@@

```{r hcl-palettes-sequentialm-0, echo = TRUE, eval = FALSE}
hcl_palettes("sequential (multi-hue)", n = 7, plot = TRUE)
```
```{r hcl-palettes-sequentialm, echo = FALSE, fig.width = 8.5, fig.height = 9.0, fig.cap = "Prespecified sequential multi-hue HCL palettes available in \\code{sequential\\_hcl()} in \\pkg{colorspace}."}
hcl_palettes("sequential (multi-hue)", n = 7, plot = TRUE, mar = c(0.1, 7, 0, 0), line = 6)
```
